The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-15 paper/ms.tex
halo photometry

Brighter \kepler stars are therefore ideal benchmark targets, as photometry can be most easily complemented by \hipparcos parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of saturated stars, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detector, spilling electrons up and down their column on the CCD and rendering these pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detector are actually downloaded, these being allocated via a competitive proposal process. The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored.

>>>>

Brighter \kepler stars are therefore ideal benchmark targets, as photometry can be most easily complemented by \hipparcos parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of saturated stars, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detector, spilling electrons up and down their column on the CCD and rendering these pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detector are actually downloaded, these being allocated via a competitive proposal process. The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored. In the K2 mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.
